---
title: "Chapter 12.2"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
library(tibble)
library(distributions3)
```

# Exercise 12.9
Refer to Exercise 12.6 and assume that the assumptions about the model prevail. The estimated standard errors of $\hat{\beta_1}$, and $\hat{\beta_2}$ are .00161, and .1862, respectively. 
\newline
\newline
**a) Determine a 95% Confidence Interval for $\beta_2$.** \newline
To obtain a $100(1 - \alpha)\%$ confidence interval for $\beta_2$, we'll use $\beta_2 \pm t_{\frac{\alpha}{2}}\frac{S}{\sqrt{S_{xx}}}$:

```{r}
bhat2 <- -1.56
t <- StudentsT(50)
lower <- bhat2 - (quantile(t, 1 - .05 / 2) * .1862)
upper <- bhat2 + (quantile(t, 1 - .05 / 2) * .1862)
paste(lower, ', ', upper)
```
b) Test $H_0$: $\beta_1 = .0125$ versus $H_1$: $\beta_1 > .0125$, with $\alpha = .05$.
When testing $H_0: \beta_1 = \beta_{10}$, the test statistic is $T = \frac{\hat{\beta_1} - \beta_{10}}{\frac{S}{\sqrt{S_{xx}}}}, d.f. = n-2$, with a rejection region $R:T \geq t_\alpha$:
```{r}
bhat1 <- .0156
t <- StudentsT(48)
test <- (bhat1 - .0125)/(.00161)
t_val <- quantile(t, 1 - .05)
paste('Test statistic:', test, 't_a:', t_val)
```
Because the test statistic (1.925) is greater than $t_{.05}$ (1.677), we reject $H_0$. 
